---
title: "Quiz 2 Week 2 R Programming Coursera"
output: rmarkdown::github_document
---
1.
Question 1

Suppose I define the following function in R

```{r}
cube <- function(x, n) {
        x^3
}
cube(3)
```

-> The number 27 is returned

2.
Question 2

The following code will produce a warning in R.

```{r}
x <- 1:10
if(x > 5) {
        x <- 0
}
```

3.
Question 3

Consider the following function

```{r}
f <- function(x) {
        g <- function(y) {
                y + z
        }
        z <- 4
        x + g(x)
}

z <- 10
f(3)
```
-> 10

4.
Question 4

Consider the following expression:

```{r}
x <- 5
y <- if(x < 3) {
        NA
} else {
        10
}
y
```
4.
Question 4

Consider the following expression:

6

What is the value of 'y' after evaluating this expression?
-> 10

5.
Question 5

Consider the following R function
```{r}
h <- function(x, y = NULL, d = 3L) {
        z <- cbind(x, d)
        if(!is.null(y))
                z <- z + y
        else
                z <- z + f
        g <- x + y / z
        if(d == 3L)
                return(g)
        g <- g + 10
        g
}
```
Which symbol in the above function is a free variable?
-> f

```{r}
h <- function(x, y = NULL, d = 3L) {
        z <- cbind(x, d)
        if(!is.null(y))
                z <- z + y
        else
                z <- z + f
        g <- x + y / z
        if(d == 3L)
                return(g)
        g <- g + 10
        g
}
```
Which symbol in the above function is a free variable?
-> f

6.
Question 6

What is an environment in R?
-> a collection of symbol/value pairs

7.
Question 7

The R language uses what type of scoping rule for resolving free variables?
-> Lexical scoping

8.
Question 8

How are free variables in R functions resolved?
-> The values of free variables are searched for in the environment in which the function was defined

9.
Question 9

What is one of the consequences of the scoping rules used in R?
-> All objects must be stored in memory

10.
Question 10

In R, what is the parent frame?
-> It is the environment in which a function was called