---
title: "Learn about the apply function family"
output: rmarkdown::github_document
---

# Lapply
- Apply the function to a list 
- Retunr a list, regardless of the class of the input
- Usually use with anonymous function
```{r}
x <- list(a = 1:5, b = rnorm(10))
lapply(x, mean)

$a
[1] 3

$b
[1] -0.0474927
 

x <- 1:4
lapply(x, runif)
# [[1]]
# [1] 0.6922116

# [[2]]
# [1] 0.6281319 0.3957540

# [[3]]
# [1] 0.1426731 0.7342085 0.8267546

# [[4]]
# [1] 0.02391304 0.86053427 0.53900690 0.21644929


```

runif is a function with n elements vector

## Sapply
- Simplied version of lapply

# Apply
- Use to evaluate a function, usually anonymous one
- Apply over a margins of an array
- Involve less typing

```{r}
str(apply)
#function (X, MARGIN, FUN, ..., simplify = TRUE)

x <- matrix(rnorm(200), 20, 10)
apply(x, 2, mean) #Keep the second dim and collapse the first one => 10 items in this vector represent 10 rows
# [1] -0.59091016 -0.15505849 -0.05137849  0.25471673  0.08686630 -0.33403661
#  [7] -0.16510079  0.25139287 -0.19626585 -0.19734054
# Take the mean on each column

apply(x, 1, sum)
#Calculate sum of each row

rowSums()
rowMeans()
colMeans()
...
```

# Mapply
- Multivariate apply of the above function

```{r}
str(mapply)
#function (FUN, ..., MoreArgs = NULL, SIMPLIFY 
#               = TRUE, USE.NAMES = TRUE)

list(rep(1, 4), rep(2, 3), rep(3,2), rep(4,1))
mapply(rep, 1:4, 4:1)
# Same result

```

# Tapply
- Useful to apply function on a subset of vector

```{r}
x <- c(rnorm(10), runif(10), rnorm(10,1))
f <- gl(3, 10)
f
tapply(x, f, mean)
#         1         2         3
# 0.4684564 0.6691001 1.1009399
# Take group mean
# Have been simplyfied


```

# Split
- Take a vector or object and a factor or list of factors
- The object will be spilted into group of factor

```{r}
split(x, f)
# $`1`
#  [1]  0.4300003  0.7141608  1.4635252  0.7070638  0.4543599  1.6778389
#  [7] -0.5929200  1.0397581 -0.9093814 -0.2998418

# $`2`
#  [1] 0.5655138 0.9520879 0.8892222 0.7891363 0.5976622 0.1350595 0.8145887
#  [8] 0.1664357 0.8492442 0.9320504

# $`3`
#  [1]  0.3187657  1.6585809 -0.4013755  1.9343462  0.7293687 -1.4389543
#  [7]  1.9436892  1.6228836  1.2888585  3.3532355


```

- It is like tapply but without the apply function on the objects

```{r}
s <- split(airquality, airquality$Month)
s
lapply(s, function(x) colMeans(x[, c("Ozone", "Solar.R", "Wind")]))
# $`5`
#    Ozone  Solar.R     Wind 
#       NA       NA 11.62258

# $`6`
#     Ozone   Solar.R      Wind
#        NA 190.16667  10.26667

# $`7`
#      Ozone    Solar.R       Wind
#         NA 216.483871   8.941935 

# $`8`
#    Ozone  Solar.R     Wind
#       NA       NA 8.793548

# $`9`
#    Ozone  Solar.R     Wind
#       NA 167.4333  10.1800

sapply(s, function(x) colMeans(x[, c("Ozone", "Solar.R", "Wind")]))
#              5         6          7        8        9
# Ozone         NA        NA         NA       NA       NA
# Solar.R       NA 190.16667 216.483871       NA 167.4333
# Wind    11.62258  10.26667   8.941935 8.793548  10.1800


#Spilting on More than One level
x <- rnorm(10)
f1 <- gl(2,5)
f2 <- gl(5,2)

f1
#  [1] 1 1 1 1 1 2 2 2 2 2
# Levels: 1 2
f2
#  [1] 1 1 2 2 3 3 4 4 5 5
# Levels: 1 2 3 4 5

interaction(f1,f2)
# [1] 1.1 1.1 1.2 1.2 1.3 2.3 2.4 2.4 2.5 2.5  
# Levels: 1.1 2.1 1.2 2.2 1.3 2.3 1.4 2.4 1.5 2.5

str(split(x, list(f1,f2)))
# List of 10
#  $ 1.1: num [1:2] -1.511 -0.151
#  $ 2.1: num(0)
#  $ 1.2: num [1:2] 1.026 -0.128
#  $ 2.2: num(0)
#  $ 1.3: num 0.732
#  $ 2.3: num 0.803
#  $ 1.4: num(0)
#  $ 2.4: num [1:2] 0.536 -1.179
#  $ 1.5: num(0)
#  $ 2.5: num [1:2] 0.0443 -0.8934

#If specified drop = TRUE, it will drop the empty level

```

# Sumary

apply() - Input: array (matrices); margin (which axis to work on); function (apply on the data)

lapply() and sapply() - Input: list; function

vapply() - like sapply() but need to specified return value 

tapply() - Input: list, vector (can have different length), factor vector, function

