# Dates and Times

## Introduction
- Dates are represented by the *Date* class
- Times are represented by the *POSIXct* or the *POSIXIt* class
- Dates are stored internally as the number of days since 1/1/1970
- Times are stored internally as the number of seconds since 1/1/1970

```{r}
x <- as.Date('1970-01-01')
x #[1] "1970-01-01"
unclass(x) #[1] 0

```

## Times
- POSIXct stores as big integer
- POSIXIt stores times as lists, useful data

- weekdays: day of the week
- months: month name
- quarters: quarter number

```{r}
x <- Sys.time()
x #[1] "2021-09-03 15:00:30 +07" 

p <- as.POSIXct(x)
p #[1] "2021-09-03 15:00:30 +07"
unclass(p) #[1] 1630656031
names(unclass(p))
# NULL

p <- as.POSIXlt(x)
unclass(p)
# $sec
# [1] 30.68955

# $min
# [1] 0

# $hour
# [1] 15

# $mday
# [1] 3

# $mon
# [1] 8

# $year
# [1] 121

# $wday
# [1] 5

# $yday
# [1] 245

# $isdst
# [1] 0

# $zone
# [1] "+07"

# $gmtoff
# [1] 25200

# attr(,"tzone")
# [1] ""    "+07" "   "
names(unclass(p))
# [1] "sec"    "min"    "hour"   "mday"   "mon"    "year"   "wday"   "yday"
# [9] "isdst"  "zone"   "gmtoff"

p$sec #[1] 30.68955


#strptime function in order your dates are written in a different format
datestring <- c("January 10, 2012 10:40", "December 9, 2011 9:10")
x <- strptime(datestring, "%B %d, %Y %H:%M")
x
#[1] "2012-01-10 10:40:00 +07" "2011-12-09 09:10:00 +07"

class(x)
#[1] "POSIXlt" "POSIXt"

x-x
#Time differences in secs
#[1] 0 0

x <- as.POSIXct("2012-01-10 10:40:00 +07")
y <- as.POSIXct("2011-12-09 09:10:00 +07", tz = "GMT")

y - x
#Time difference of -31.77083 days  
```