---
title: "Learn about how to read and write data in R"
output: rmarkdown::github_document
---
# Reading Data
- There are a few principal functions reading data into R

```{r}
#Reading tabular data
read.table(file, {utils}) 
read.csv(file, {utils})

# Notice that utils can be header, sep, dec, row.names, col.names, etc
```
More can be found here: [URL](https://stat.ethz.ch/R-manual/R-devel/library/utils/html/read.table.html)

```{r}
#Reading lines for text file
readLines() 

#For reading in R code files(inverse of dump)
source() and dget() for reading source code R file


```
More about readLines: [URL](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/readLines)
Detail description: [URL](https://datag.org/resources/documents/december-2017/12-debarros-learn-to-use-r-reading-source-data-in-r/file)

- ```load()``` for reading in saved workspace
- ```unserialize()``` for reading binary object into R

# Writing Data
```{r}
write.table()
writeLines()
dump()
dput()
save()
serialize()
```

- Pairing with reading analog

## Reading data file with read.table
- Commonly used function for reading data.
- Args: 
    + file name
    + header, sep, colClasses, norows, comment.char.a, skip, stringsAsFactors

```{r}
data <- read.table("foo.txt")

```
- Can be automatically read
- Skip lines that begin with a #
- The same with read.csv with the difference between the two with sep = ","

#### Large dataset
- Read the help page of read.table for hints
- Make rough calculation of the memory required due to the physically storing
- Set comment.char = "" is there are no commented lines in your files

- Use the colClasses args can make it run much faster, may be twice
    + To use, need to know class of each column in your data frame

```{r}
initial <- read.table("database.txt", nrows = 100)
classes <- sapply(initial, class)
tabAll <- read.table("database.txt", colClasses = classes)
```
- Set nrows because it helps with memory usage. Can have a mild overestimate
- Can use wc tool in Unix to calculate the number of lines in a files

Need to know before getting started
- How much physical RAM?
- What other applications are in use?
- Are there other users logged into the same system?
- What operating system?
- Is the OS 32 or 64 bit? 64 bits provide more access to memory if you have more RAM

- From rows, cols, type of data calculating the number of memory is required to store this data frame?
- Numeric 8 bytes



# Some command

```ls()``` is for listing all variable in the env
```getwd()``` to take current working directory setwd() for setting working env
```list.files() or dir()``` is dor listing all files in working directory'

```files.create()``` is for creating file in current workspace
```{r}
file.rename(from, to)
file.copy(forom, to)
file.remove(name)

file.exists(name)
file.info(name)

file.path(name) #Get the path to that file

dir.create(file.path("testdir2", "testdir3"), recursive = TRUE) #To create a testdir3 inside testdir 2 in the current workspace
```