---
title: "Learn about how subsetting work in R"
output: rmarkdown::github_document
---

## Vectors
There are 3 ways that can be extract subsets of R objects
    1. [ returns an object with the same class as the original
    2. [[ is used to extract elements of a list or a data frame
    3. $ is used to extract elements of a list or data frame by name, semantics are similar to hat of [[

```{r}
x <- c("a", "v", "v", "d", "e")
x[1]
#[1] "a"
x[2]
#[1] "v"
x[1:4]
#[1] "a" "v" "v" "d"
x[x > "a"]
#[1] "v" "v" "d" "e"
u <- x > "a"
u
#[1] FALSE  TRUE  TRUE  TRUE  TRUE



```

## Lists

```{r}
x <- list(foo = 1:4, bar = 0.4)
x[1]
# $foo
# [1] 1 2 3 4

x[[1]]
# > x[[1]]
# [1] 1 2 3 4

x$bar
#[1] 0.4

x["bar"]
# $bar
# [1] 0.4

x[c(1,2)]
# $foo
# [1] 1 2 3 4

# $bar
# [1] 0.4

x <- list(a= list(10,12,14), b= c(3.14, 2.81))
x[c(1,3)]
# $a
# $a[[1]]
# [1] 10

# $a[[2]]
# [1] 12

# $a[[3]]
# [1] 14


# $<NA>
# NULL

x[[c(1,3)]] #[1] 14

x[[1]][[3]] #[1] 14

x[[c(2,1)]] #[1] 3.14


```

## Matrices

- The first index is row, second is col

```{r}
x <- matrix(1:6, 2, 3)
x[1,2]
#[1] 3

x[2,1]
# [1] 2

x[1, ]
#[1] 1 3 5
# I want the first row
x[, 2]
#[1] 3 4
#i want the 2 col
x[1,2]
#[1] 3
x[1, 2, drop = FALSE]
#     [,1]
# [1,]    3
# To return the full dimension woithout droping
```

## Removing NA values
- Create logical vector to indicate NAs

```{r}
x <- c(1, 2, NA, 4, NA, 5)
bad <- is.na(x)
x[!bad]
# [1] 1 2 4 5

y <- c("a", "b", NA, "d", NA, "t")
good <- complete.cases(x, y)
good 
# [1]  TRUE  TRUE FALSE  TRUE FALSE  TRUE
x[good] #[1] 1 2 4 5
y[good] #[1] "a" "b" "d" "t"
```
