# Data Types
Everything in R are objects

- character
- numberic
- integer
- complex
- logical

Everything in vector must to be the same class.
List can have multiple class elements.

### Numbers
- R thinks this as a numberic objects
- Inf for infinity
    + 1 / 0 == Inf
    + 1 / Inf == 0

- NaN is an undefined value

### Attributes
- Parts of objects in R
- Objects can have or not have attributes:
    + names, dimnames
    + dimensions (matrices, array)
    + class
    + length
    + other user-defined attributes/metadata
- Can be accessed using the ``` attributes() ``` function to modify.

### c()
- Can used to create vectors of objects.

```{r include=FALSE}
x <- c(0.5,0.6) #numberic
x <- c(TRUE, FALSE) #logical
print(x)
```

### Mixing objects

```{r}
y <- c(1.7, 'a')     #[1] "1.7" "a"
y <- c(TRUE,2)  #[1] 1 2
y <- c('a',TRUE)    #[1] "a"    "TRUE"
print(y)
```

Won't get error but it will change your objects' type.

### Explicit Coercion
- Use ``` as.* ```   function to convert one class to a another 
```{r}
x <- 0:6
class(x) #[1] "integer"
as.numeric(x) # [1] 0 1 2 3 4 5 6
as.logical(x) # [1] FALSE  TRUE  TRUE  TRUE  TRUE  TRUE  TRUE
as.character(x) # [1] "0" "1" "2" "3" "4" "5" "6"
```

```{python}
x = 5
print(x)
class(x)
```

But when you convert character to numberic, it will be NA
```{r}
x <- c('a', 'b', 'c')
as.numeric(x) 
#[1] NA NA NA
#Warning message:
#NAs introduced by coercion
```

### Lists
- Handy when need to be contain elements of different classes

```{r}
x <- list(1, 'a', TRUE, 1+4i)
print(x)
# Result
# [[1]]
# [1] 1

# [[2]]
# [1] "a"

# [[3]]
# [1] TRUE

# [[4]]
# [1] 1+4i
```

### Matrices
- Special types of vectors
- Have special attributes as dimensions
- nrows and ncol

```{r}
m <- matrix(nrow = 2, ncol = 3)
m
#      [,1] [,2] [,3]
# [1,]   NA   NA   NA
# [2,]   NA   NA   NA
dim(m) #[1] 2 3
attributes(m)
# $dim
# [1] 2 3
```

- All the number are inserted into matrix by column 

```{r}
m <- matrix(1:6, nrow = 2, ncol = 1)
m
#      [,1]
# [1,]    1
# [2,]    2

m <- matrix(1:6, nrow = 2, ncol = 3)
m
#      [,1] [,2] [,3]
# [1,]    1    3    5
# [2,]    2    4    6

m <- matrix(1:6, nrow = 2, ncol = 4)
# Warning message:
# In matrix(1:6, nrow = 2, ncol = 4) :
#   data length [6] is not a sub-multiple or multiple of the number of columns [4]

```

- You can also create the matrice directly from the available vector by adding the dimension attribute

```{r}
m <- 1:10
m #[1]  1  2  3  4  5  6  7  8  9 10
dim(m) <- c(2,5)
m
#      [,1] [,2] [,3] [,4] [,5]
# [1,]    1    3    5    7    9
# [2,]    2    4    6    8   10

vector <- c(1:10)
vector #[1]  1  2  3  4  5  6  7  8  9 10
dim(vector) <- c(5,2)
vector
#      [,1] [,2]
# [1,]    1    6
# [2,]    2    7
# [3,]    3    8
# [4,]    4    9
# [5,]    5   10
```

- Another way to create a matrice is to bind column or bind row
- with ```{r} cbind()``` and ```{r} rbind()```

```{r}
x <- 1:3
y <- 10:12
cbind(x,y)
#      x  y
# [1,] 1 10
# [2,] 2 11
# [3,] 3 12
rbind(x,y)
#   [,1] [,2] [,3]
# x    1    2    3
# y   10   11   12
```

### Factors
- Two types of factors
    + Unordered
    + Ordered
        1. Not really numeric
        2. May be professor, vice-professor, ...
        3. Label for fitting linear model

- Like an integer vector which each of them has label
- Treated specially by modelling function like ```{r} lm() and glm()```
- It is self-describing
- For example: a variable that has values 'Male' or 'Female' is better than a variable that has value 1 or 2

```{r}
x <- factor(c("yes", "yes", 'no', 'yes', 'no'))
x
# [1] yes yes no  yes no
# Levels: no yes

table(x)
# x
#  no yes
#   2   3

unclass(x) #Use for displaying the integer vector with level of the attribute of no and yes
#This is for strips out the class for a vector
#You can see the underlying integer vector
# 'yes' is coded as 2
# 'no' is coded as 1
# [1] 2 2 1 2 1
# attr(,"levels")
# [1] "no"  "yes"

#You can define the level attribute with expression like this
x <- factor(c("yes", "yes", "no", "yes", "no"), 
    levels = c("yes","no" ))
x
# [1] yes yes no  yes no
# Levels: yes no

#The baseline level be the first level it encounter
```

### Missing values
- Denote by NA (everything that is not used with NaN) or NaN (undefined mathematical operations)
- ```is.na()``` is used to test objects if they are NA
- ```is.nan()``` is used to test for NaN

- NA values have a class also, so there are integer NA, character NA, etc
- A NaN value is also NA but the converse is not true
- NA is a more general term -> NaN can be check by ```is.na()```


### Data Frames
- Key data type for tabular 
- Special *type of list* where every element of the list has to have the same length -> due to the rows
- Each element of the list can be thought of as a column and the n of length is n of rows
- Unlike matrices, data frames can be store different classes of objects in each column (like lists)

- Data frames also have a special attribute called ```row.names```
- Data frames usually created by calling ```{r} read.table()``` or ```{r} read.csv()```
- Can be converted to a matrix by calling ```{r} data.matrix()```

```{r}
x <- data.frame(foo = 1:4, bar = c(T, T, F, F))
x
#   foo   bar
# 1   1  TRUE
# 2   2  TRUE
# 3   3 FALSE
# 4   4 FALSE

nrow(x) #[1] 4
ncol(x) #[1] 2
```

**Python**
- Data Frame in Python is quite the same semantic meaning
- Need to import pandas

```{python}
import pandas as pd
# first create a list
lst = {'name': ['Nhu', 'Minh']}
df = pd.DataFrame(lst)
print(df)
```

### Names
- R objects can also ave names, which is very useful for writing readable code and self-describing objects

```{r}
x <- 1:3
names(x) # NULL
names(x) <- c("foo", 'bar', 'norf')
x
#  foo  bar norf
#    1    2    3
names(x) #[1] "foo"  "bar"  "norf"
```

```{r}
x <- 1:6
names(x) # NULL
names(x) <- c("foo", 'bar', 'norf')
x
#  foo  bar norf <NA> <NA> <NA>
#    1    2    3    4    5    6
names(x) #[1] "foo"  "bar"  "norf" NA     NA     NA
```

```{r}
x <- list(a = 1, b = 2, c = 3)
x
# $a
# [1] 1

# $b
# [1] 2

# $c
# [1] 3
```

- Matrices can have name to, this is called dimnames

```{r}
m <- matrix(1:4, nrow = 2, ncol = 2)
dimnames(m) <- list(c('a','b'), c('c','d'))
m
#   c d
# a 1 3
# b 2 4
```

